Computer Science House By-Laws

### 2017-09-28 bylaws.tex
By-Law VI: Use of Intellectual Property
major House project -> major project
Add table of contents to articles/bylaws (#118)
Reduced scope of branch - removed subjective expectation
major House project -> major project (#119)
bylaws: Update standard operating session length
This reflects the new semester schedule RIT has switched to.

\documentclass{article}
\providecommand{\RevisionInfo}{}
% The xr package allows external references
\usepackage{xr-hyper}
\usepackage{hyperref}

@@

% Use \article for articles and \asection for sections of articles.
% Automatically provide labels with the same article or section title.
\newcommand{\bylaw}[1]{\section{#1} \label{#1}}
\newcommand{\bsection}[1]{\subsection{#1} \label{#1}}
\newcommand{\bsubsection}[1]{\subsubsection{#1} \label{#1}}
\renewcommand{\thesection}{By-Law \Roman{section}}
\renewcommand{\thesubsection}{Section \arabic{section}.\Alph{subsection}}
\renewcommand{\thesubsubsection}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}}

@@

@@

% BY-LAW II - GENERAL OPERATIONS OF THE HOUSE
\bylaw{General Operations of the House}
\bsection{Standard Operating Session}
The Standard Operating Session for Computer Science House is during the thirty weeks of Fall and Spring semesters.
The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions.
Unless explicitly stated otherwise, the requirements and expectations defined in the constitution are for the Standard Operating Session.

@@

\bsection{Expectations of House Members}
Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least twenty-five (25) of the permanent director meetings.
Members are also required to actively participate in a majority of House activities.
\\* \\*
The member must participate significantly in at least one major House project during the academic year.
The member is required to submit a description for this major project to the Executive Board for approval.
As an option to this requirement, the member may instead assist on a large number of House activities and projects.
However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
This participation will be evaluated by the Executive Board.

>>>>

\documentclass{article}
\providecommand{\RevisionInfo}{}
% The xr package allows external references
\usepackage{xr-hyper}
\usepackage{hyperref}
% Reformat section titles
\usepackage{titlesec}

@@

% Use \article for articles and \asection for sections of articles.
% Automatically provide labels with the same article or section title.
\newcommand{\bylaw}[1]{\section{#1} \label{#1}}
\newcommand{\bsection}[1]{\subsection{#1} \label{#1}}
\newcommand{\bsubsection}[1]{\subsubsection{#1} \label{#1}}
\renewcommand{\thesection}{\Roman{section}}
\renewcommand{\thesubsection}{\arabic{section}.\Alph{subsection}}
\renewcommand{\thesubsubsection}{\arabic{section}.\Alph{subsection}.\arabic{subsubsection}}
\titleformat{\section}{\normalfont\Large\bfseries}{By-Law \thesection}{1em}{}
\titleformat{\subsection}{\normalfont\large\bfseries}{Section \thesubsection}{1em}{}

@@

\tableofcontents

@@

% BY-LAW II - GENERAL OPERATIONS OF THE HOUSE
\bylaw{General Operations of the House}
\bsection{Standard Operating Session}
The Standard Operating Session for Computer Science House is during the twenty-eight weeks of Fall and Spring semesters.
The Summer Sessions, Intersessions, Institute breaks, and all end of Semester Exam Weeks are considered non-standard operating sessions.
Unless explicitly stated otherwise, the requirements and expectations defined in the constitution are for the Standard Operating Session.

@@

\bsection{Expectations of House Members}
Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least twenty-five (25) of the permanent director meetings.
Members are also required to actively participate in a majority of House activities.
\\* \\*
The member must participate significantly in at least one major project during the academic year.
The member is required to submit a description for this major project to the Executive Board for approval.
As an option to this requirement, the member may instead assist on a large number of House activities and projects.
However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
This participation will be evaluated by the Executive Board.
